---
title: "Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    df_print: paged
always_allow_html: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

## Calculation theory
### Optimal fracture parameters

To determine the necessary relationships between fracture length and fracture width when planning fracturing, the most important parameter is the dimensionless proppant number $N_{prop}$.  

Dimensionless proppant number:
$$N_{prop}=I_x^2\cdot C_{fD}=\frac{2k_f}{k}\cdot\frac{V_{prop}}{V_{res}}$$  

Dimensionless fracture conductivity: 
$$C_{fD}=\frac{k_f\cdot w}{k\cdot x_f}$$
Fracture penetration:
$$I_x=\frac{2x_f}{x_e}$$
Optimal half length:
$$x_f=\left(\frac{V_fk_f}{C_{fD,opt}hk}\right)^{1/2}$$
Optimal propped width:
$$w=\left(\frac{C_{fD,opt}V_fk}{hk_f}\right)^{1/2}=\frac{V_f}{x_fh}$$
Dimensionless productivity index:  
$$J_d=\frac{1}{\ln{\left[\frac{0,472\ r_e}{r_w}\right]}+s_f}$$

### Actual proppant placement
In the fracture design application, the PKN (Perkins-Kern-Nordgren) model was used as a fracture propagation model.    
    
The maximum width of the ellipse in the bottomhole zone:
$$w_0(x)=3,57\left(\frac{\mu q_ix_f}{E'}\right)^{1/4}$$
Average fracture width:
$$\bar{w}=0,628 \cdot w_{w,0}$$

### Treatment mode parameters

Injection fluid volume:  
$$V_i=q_it_e$$
Fluid efficiency:  
$$\eta_i=\frac{h_fx_f\bar{w_e}}{V_i}$$
Exponent of added proppant concentration of the injected proppant:
$$\varepsilon\ =\ \frac{1-\eta_e}{1+\eta_e}$$
The volume of the "pad" and the time for its pumping:
$$V_{pad}\ =\varepsilon V_i$$
$$t_{pad}\ =\varepsilon t_e$$
Areal concentration of proppant after fracture closure:
$$c_s=\frac{M_{act}}{h_f\ \cdot2x_f}$$
### Calculation results


```{r}
                                    data <- df_en()
                                    colnames(data)<-c('Parameter','Value')
                                    knitr::kable(data,
                                               caption = "Optimal placement")
                                     br()
```


```{r}
                                    data <- dfA_en()
                                    colnames(data)<-c('Parameter','Value')
                                    knitr::kable(data,
                                               caption = "Actual placement")
                                    br()
```

```{r}
                                    data <- dfR_en()
                                    colnames(data)<-c('Parameter','Value')
                                    knitr::kable(data,
                                               caption = "Treatment mode")
                                    br()
```



<!-- ### Комментарии к расчёту -->

<!-- ```{r Interval2, warning = FALSE} -->
<!-- note_in_md_word(input$markdowninput) -->
<!-- ``` -->
